Path Analysis Data Development - Chapter 2

### 2016-08-26 sem-data-development.Rmd
Update lagged temperature variables.

# Join the environmental data to the bay laurel infection data
umca_plots <- left_join(umca_plots, plots_env, by = "plotid")
summary(umca_plots)
# filter(umca_plots, is.na(lon_utm))
# NAs due to no topo data for abandoned SUGAR02; remove SUGAR02
# umca_plots <- na.omit(umca_plots)
umca_plots <- rename(umca_plots, sample_year = year)
# umca_plots$plotid <- tolower(umca_plots$plotid)
umca_in_plots <- left_join(umca_in_plots, plots_env, by = "plotid")
umca_in_plots <- rename(umca_in_plots, sample_year = year)
# Join rainy season and summer temperatures to bay laurel infection data.
## I need to rename temperature variables to differentiate rainy vs. dry season
rs_temps <- as.tbl(rs_temps)
rs_temps$plotid <- tolower(rs_temps$plotid)
summary(rs_temps)
rs_temps <- rename(rs_temps, 
                   hrs_14_20_rs = hrs_14_20, hrs_abv25rs = hrs_abv25,
                   hrs_abv20_rs = hrs_abv20, hrs_blw10rs = hrs_blw10,
                   avg_tmax_rs = avg_tmax, avg_tmin_rs = avg_tmin)

summer_temps <- as.tbl(summer_temps)
summer_temps$plotid <- tolower(summer_temps$plotid)
summary(summer_temps)
summer_temps <- rename(summer_temps, 
                       hrs_abv25ds = hrs_abv25, hrs_abv20ds = hrs_abv20,
                       hrs_blw18ds = hrs_blw18, avg_tmax_ds = avg_tmax,
                       avg_tmin_ds = avg_tmin)

@@

hrsblw14_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrsblw14_wet))
avgtmax_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, avgtmax_wet))
hrs1422_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrs1422_wet))
wet_hrs_lag <- select(wet_hrs, plotid, sample_year)
wet_hrs_lag <- wet_hrs_lag %>% 
      mutate(sample_year_minus1 = sample_year - 1,
             sample_year_minus2 = sample_year - 2,
             sample_year_minus3 = sample_year - 3)

@@

@@

@@

@@

@@

@@

hrs1420_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_14_20_rs))
avgtmax_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, avg_tmax_rs))
hrsabv20_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_abv20_rs))
hrsblw10_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_blw10rs))

@@

@@

@@

@@

@@

@@

@@

hrs_abv25ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, hrs_abv25ds))
avg_tmax_ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, avg_tmax_ds))
hrs_blw18ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, hrs_blw18ds))

@@

@@

## Number of dry-season hours below 18 C lagged ####
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw18ds_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrs_blw18ds_tminus1 = hrs_blw18ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw18ds_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrs_blw18ds_tminus2 = hrs_blw18ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw18ds_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrs_blw18ds_tminus3 = hrs_blw18ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw18ds_lag,
                              by = c("plotid", "sample_year"="sample_year"))

## ####
summer_temps_lag <- select(summer_temps_lag, plotid, sample_year, starts_with("hrs"), starts_with("avg"))
summer_temps_lag <- summer_temps_lag %>% 
      mutate(
            avg_hrsblw18_ds_tminus1 = rowMeans(cbind(hrs_blw18ds, hrs_blw18ds_tminus1)),
             avg_hrsblw18_ds_tminus2 = rowMeans(cbind(hrs_blw18ds, hrs_blw18ds_tminus1, hrs_blw18ds_tminus2)),
             avg_hrsblw18_ds_tminus3 = rowMeans(cbind(hrs_blw18ds, hrs_blw18ds_tminus1, hrs_blw18ds_tminus2, hrs_blw18ds_tminus3)),
             avg_hrsblw18_ds_t1t2 = rowMeans(cbind(hrs_blw18ds_tminus1, hrs_blw18ds_tminus2)),

@@

>>>>

# Join the environmental data to the bay laurel infection data
umca_plots <- left_join(umca_plots, plots_env, by = "plotid")
summary(umca_plots)
# filter(umca_plots, is.na(lon_utm))
# NAs due to no topo data for abandoned SUGAR02; remove SUGAR02
# umca_plots <- na.omit(umca_plots)
umca_plots <- rename(umca_plots, sample_year = year)
# umca_plots$plotid <- tolower(umca_plots$plotid)
umca_in_plots <- left_join(umca_in_plots, plots_env, by = "plotid")
umca_in_plots <- rename(umca_in_plots, sample_year = year)
# Join rainy season and summer temperatures to bay laurel infection data.
## I need to rename temperature variables to differentiate rainy vs. dry season
rs_temps <- as.tbl(rs_temps)
rs_temps$plotid <- tolower(rs_temps$plotid)
summary(rs_temps)
rs_temps <- rename(rs_temps, 
                   hrs_14_20_rs = hrs_14_20, hrs_10_20_rs = hrs_10_20,
                   hrs_abv25rs = hrs_abv25, hrs_abv20_rs = hrs_abv20,
                   hrs_blw20rs = hrs_blw20, hrs_blw10rs = hrs_blw10,
                   hrs_blw14rs = hrs_blw14, avg_tmax_rs = avg_tmax,
                   avg_tmin_rs = avg_tmin)

summer_temps <- as.tbl(summer_temps)
summer_temps$plotid <- tolower(summer_temps$plotid)
summary(summer_temps)
summer_temps <- rename(summer_temps, 
                       hrs_abv25ds = hrs_abv25, hrs_abv20ds = hrs_abv20,
                       hrs_blw20ds = hrs_blw20, avg_tmax_ds = avg_tmax,
                       avg_tmin_ds = avg_tmin)

@@

hrsblw14_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrsblw14_wet))
hrs1422_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrs1422_wet))
hrsabv22_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrsabv22_wet))
hrsblw22_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrsblw22_wet))
hrsblw10_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrsblw10_wet))
hrs1020_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrs1020_wet))
hrs1022_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrs1022_wet))
hrsabv20_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrsabv20_wet))
hrsblw20_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, hrsblw20_wet))

avgtmax_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, avgtmax_wet))
avgtmin_wet_lag <- as.tbl(select(wet_hrs, plotid, sample_year, avgtmin_wet))

wet_hrs_lag <- select(wet_hrs, plotid, sample_year)
wet_hrs_lag <- wet_hrs_lag %>% 
      mutate(sample_year_minus1 = sample_year - 1,
             sample_year_minus2 = sample_year - 2,
             sample_year_minus3 = sample_year - 3)

@@

## Number of wet-hours below 20 C lagged ####
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw20_wet_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrsblw20_wet_tminus1 = hrsblw20_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw20_wet_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrsblw20_wet_tminus2 = hrsblw20_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw20_wet_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrsblw20_wet_tminus3 = hrsblw20_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw20_wet_lag,
                by = c("plotid", "sample_year"="sample_year"))

## Number of wet-hours below 10 C lagged ####
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw10_wet_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrsblw10_wet_tminus1 = hrsblw10_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw10_wet_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrsblw10_wet_tminus2 = hrsblw10_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw10_wet_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrsblw10_wet_tminus3 = hrsblw10_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrsblw10_wet_lag,
                by = c("plotid", "sample_year"="sample_year"))

@@

## Average daily minimum temperature on wet days lagged ####
wet_hrs_lag <- left_join(wet_hrs_lag, avgtmin_wet_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(avgtmin_wet_tminus1 = avgtmin_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, avgtmin_wet_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(avgtmin_wet_tminus2 = avgtmin_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, avgtmin_wet_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(avgtmin_wet_tminus3 = avgtmin_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, avgtmin_wet_lag,
                by = c("plotid", "sample_year"="sample_year"))

@@

## Number of hours 10-20 C on wet days ####
wet_hrs_lag <- left_join(wet_hrs_lag, hrs1020_wet_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrs1020_wet_tminus1 = hrs1020_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrs1020_wet_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrs1020_wet_tminus2 = hrs1020_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrs1020_wet_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrs1020_wet_tminus3 = hrs1020_wet)
wet_hrs_lag <- left_join(wet_hrs_lag, hrs1020_wet_lag,
                by = c("plotid", "sample_year"="sample_year"))

@@

            avg_hrsblw10_wet_tminus1 = rowMeans(cbind(hrsblw10_wet, hrsblw10_wet_tminus1)),
             avg_hrsblw10_wet_tminus2 = rowMeans(cbind(hrsblw10_wet, hrsblw10_wet_tminus1, hrsblw10_wet_tminus2)),
             avg_hrsblw10_wet_tminus3 = rowMeans(cbind(hrsblw10_wet, hrsblw10_wet_tminus1, hrsblw10_wet_tminus2, hrsblw10_wet_tminus3)),

            avg_hrsblw20_wet_tminus1 = rowMeans(cbind(hrsblw20_wet, hrsblw20_wet_tminus1)),
             avg_hrsblw20_wet_tminus2 = rowMeans(cbind(hrsblw20_wet, hrsblw20_wet_tminus1, hrsblw20_wet_tminus2)),
             avg_hrsblw20_wet_tminus3 = rowMeans(cbind(hrsblw20_wet, hrsblw20_wet_tminus1, hrsblw20_wet_tminus2, hrsblw20_wet_tminus3)),

@@

            avg_hrs1020_wet_t_t1 = rowMeans(cbind(hrs1020_wet, hrs1020_wet_tminus1)),
             avg_hrs1020_wet_t_t1t2 = rowMeans(cbind(hrs1020_wet, hrs1020_wet_tminus1, hrs1020_wet_tminus2)),
             avg_hrs1020_wet_t1t2 = rowMeans(cbind(hrs1020_wet_tminus1, hrs1020_wet_tminus2)),

@@

hrs1420_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_14_20_rs))
hrs1020_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_10_20_rs))
avgtmin_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, avg_tmin_rs))
avgtmax_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, avg_tmax_rs))
hrsabv20_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_abv20_rs))
hrsblw10_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_blw10rs))
hrsblw14_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_blw14rs))
hrsblw20_rs_lag <- as.tbl(select(rs_temps, plotid, sample_year, hrs_blw20rs))

@@

## Number of rainy season hours 10-20 C ####
rs_temps_lag <- left_join(rs_temps_lag, hrs1020_rs_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrs1020_rs_tminus1 = hrs_10_20_rs)
rs_temps_lag <- left_join(rs_temps_lag, hrs1020_rs_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrs1020_rs_tminus2 = hrs_10_20_rs)
rs_temps_lag <- left_join(rs_temps_lag, hrs1020_rs_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrs1020_rs_tminus3 = hrs_10_20_rs)
rs_temps_lag <- left_join(rs_temps_lag, hrs1020_rs_lag,
                by = c("plotid", "sample_year"="sample_year"))

@@

## Average daily minimum temperature during rainy season lagged ####
rs_temps_lag <- left_join(rs_temps_lag, avgtmin_rs_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(avgtmin_rs_tminus1 = avg_tmin_rs)
rs_temps_lag <- left_join(rs_temps_lag, avgtmin_rs_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(avgtmin_rs_tminus2 = avg_tmin_rs)
rs_temps_lag <- left_join(rs_temps_lag, avgtmin_rs_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(avgtmin_rs_tminus3 = avg_tmin_rs)
rs_temps_lag <- left_join(rs_temps_lag, avgtmin_rs_lag,
                by = c("plotid", "sample_year"="sample_year"))

@@

## Number of hours below 20 C during rainy season lagged ####
rs_temps_lag <- left_join(rs_temps_lag, hrsblw20_rs_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrsblw20_rs_tminus1 = hrs_blw20rs)
rs_temps_lag <- left_join(rs_temps_lag, hrsblw20_rs_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrsblw20_rs_tminus2 = hrs_blw20rs)
rs_temps_lag <- left_join(rs_temps_lag, hrsblw20_rs_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrsblw20_rs_tminus3 = hrs_blw20rs)
rs_temps_lag <- left_join(rs_temps_lag, hrsblw20_rs_lag,
                by = c("plotid", "sample_year"="sample_year"))

## Number of hours below 14 C during rainy season lagged ####
rs_temps_lag <- left_join(rs_temps_lag, hrsblw14_rs_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrsblw14_rs_tminus1 = hrs_blw14rs)
rs_temps_lag <- left_join(rs_temps_lag, hrsblw14_rs_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrsblw14_rs_tminus2 = hrs_blw14rs)
rs_temps_lag <- left_join(rs_temps_lag, hrsblw14_rs_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrsblw14_rs_tminus3 = hrs_blw14rs)
rs_temps_lag <- left_join(rs_temps_lag, hrsblw14_rs_lag,
                by = c("plotid", "sample_year"="sample_year"))

@@

            avgtmin_rs_t_t1 = rowMeans(cbind(avg_tmin_rs, avgtmin_rs_tminus1)),
             avgtmin_rs_t_t1t2 = rowMeans(cbind(avg_tmin_rs, avgtmin_rs_tminus1, avgtmin_rs_tminus2)),
             avgtmin_rs_t_t1t2t3 = rowMeans(cbind(avg_tmin_rs, avgtmin_rs_tminus1, avgtmin_rs_tminus2, avgtmin_rs_tminus3)),
             avgtmin_rs_t1t2 = rowMeans(cbind(avgtmin_rs_tminus1, avgtmin_rs_tminus2)),

@@

            avg_hrs1020_rs_tminus1 = rowMeans(cbind(hrs_10_20_rs, hrs1020_rs_tminus1)),
             avg_hrs1020_rs_tminus2 = rowMeans(cbind(hrs_10_20_rs, hrs1020_rs_tminus1, hrs1020_rs_tminus2)),
             avg_hrs1020_rs_tminus3 = rowMeans(cbind(hrs_10_20_rs, hrs1020_rs_tminus1, hrs1020_rs_tminus2, hrs1020_rs_tminus3)),
             avg_hrs1020_rs_t1t2 = rowMeans(cbind(hrs1020_rs_tminus1, hrs1020_rs_tminus2)),

@@

            avg_hrsblw14_rs_tminus1 = rowMeans(cbind(hrs_blw14rs, hrsblw14_rs_tminus1)),
             avg_hrsblw14_rs_tminus2 = rowMeans(cbind(hrs_blw14rs, hrsblw14_rs_tminus1, hrsblw14_rs_tminus2)),
             avg_hrsblw14_rs_tminus3 = rowMeans(cbind(hrs_blw14rs, hrsblw14_rs_tminus1, hrsblw14_rs_tminus2, hrsblw14_rs_tminus3)),
             avg_hrsblw14_rs_t1t2 = rowMeans(cbind(hrsblw14_rs_tminus1, hrsblw14_rs_tminus2)),

            avg_hrsblw20_rs_tminus1 = rowMeans(cbind(hrs_blw20rs, hrsblw20_rs_tminus1)),
             avg_hrsblw20_rs_tminus2 = rowMeans(cbind(hrs_blw20rs, hrsblw20_rs_tminus1, hrsblw20_rs_tminus2)),
             avg_hrsblw20_rs_tminus3 = rowMeans(cbind(hrs_blw20rs, hrsblw20_rs_tminus1, hrsblw20_rs_tminus2, hrsblw20_rs_tminus3)),
             avg_hrsblw20_rs_t1t2 = rowMeans(cbind(hrsblw20_rs_tminus1, hrsblw20_rs_tminus2)),

@@

hrs_abv25ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, hrs_abv25ds))
hrs_abv20ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, hrs_abv20ds))
hrs_blw20ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, hrs_blw20ds))
avg_tmax_ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, avg_tmax_ds))
avg_tmin_ds_lag <- as.tbl(select(summer_temps, plotid, sample_year, avg_tmin_ds))

@@

## Number of dry-season hours above 20 C lagged ####
summer_temps_lag <- left_join(summer_temps_lag, hrs_abv20ds_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrs_abv20ds_tminus1 = hrs_abv20ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_abv20ds_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrs_abv20ds_tminus2 = hrs_abv20ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_abv20ds_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrs_abv20ds_tminus3 = hrs_abv20ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_abv20ds_lag,
                              by = c("plotid", "sample_year"="sample_year"))

@@

## Average daily minimum temperature during dry-season lagged ####
summer_temps_lag <- left_join(summer_temps_lag, avg_tmin_ds_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(avg_tmin_ds_tminus1 = avg_tmin_ds)
summer_temps_lag <- left_join(summer_temps_lag, avg_tmin_ds_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(avg_tmin_ds_tminus2 = avg_tmin_ds)
summer_temps_lag <- left_join(summer_temps_lag, avg_tmin_ds_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(avg_tmin_ds_tminus3 = avg_tmin_ds)
summer_temps_lag <- left_join(summer_temps_lag, avg_tmin_ds_lag,
                              by = c("plotid","sample_year"="sample_year"))

## Number of dry-season hours below 20 C lagged ####
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw20ds_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(hrs_blw20ds_tminus1 = hrs_blw20ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw20ds_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(hrs_blw20ds_tminus2 = hrs_blw20ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw20ds_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(hrs_blw20ds_tminus3 = hrs_blw20ds)
summer_temps_lag <- left_join(summer_temps_lag, hrs_blw20ds_lag,
                              by = c("plotid", "sample_year"="sample_year"))

## ####
summer_temps_lag <- select(summer_temps_lag, plotid, sample_year, starts_with("hrs"), starts_with("avg"))
summer_temps_lag <- summer_temps_lag %>% 
      mutate(
            avg_hrsblw20_ds_tminus1 = rowMeans(cbind(hrs_blw20ds, hrs_blw20ds_tminus1)),
             avg_hrsblw20_ds_tminus2 = rowMeans(cbind(hrs_blw20ds, hrs_blw20ds_tminus1, hrs_blw20ds_tminus2)),
             avg_hrsblw20_ds_tminus3 = rowMeans(cbind(hrs_blw20ds, hrs_blw20ds_tminus1, hrs_blw20ds_tminus2, hrs_blw20ds_tminus3)),
             avg_hrsblw20_ds_t1t2 = rowMeans(cbind(hrs_blw20ds_tminus1, hrs_blw20ds_tminus2)),

@@

            avgtmin_ds_t_t1 = rowMeans(cbind(avg_tmin_ds, avg_tmin_ds_tminus1)),
             avgtmin_ds_t_t1t2 = rowMeans(cbind(avg_tmin_ds, avg_tmin_ds_tminus1, avg_tmin_ds_tminus2)),
             avgtmin_ds_t_t1t2t3 = rowMeans(cbind(avg_tmin_ds, avg_tmin_ds_tminus1, avg_tmin_ds_tminus2, avg_tmin_ds_tminus3)),
             avgtmin_ds_t1t2 = rowMeans(cbind(avg_tmin_ds_tminus1, avg_tmin_ds_tminus2)),

            avg_hrsabv20_ds_tminus1 = rowMeans(cbind(hrs_abv20ds, hrs_abv20ds_tminus1)),
             avg_hrsabv20_ds_tminus2 = rowMeans(cbind(hrs_abv20ds, hrs_abv20ds_tminus1, hrs_abv20ds_tminus2)),
             avg_hrsabv20_ds_tminus3 = rowMeans(cbind(hrs_abv20ds, hrs_abv20ds_tminus1, hrs_abv20ds_tminus2, hrs_abv20ds_tminus3)),
             avg_hrsabv20_ds_t1t2 = rowMeans(cbind(hrs_abv20ds_tminus1, hrs_abv20ds_tminus2)),
